A thesis draft

### 2018-11-16 res/sections/25-Tests.tex
Fix graph description
Minor english fixes

Regarding the overall system responsivness, a metric we considered worth to 
test was the VNF start up time in a docker environment versus one virtualized 
through a common virtual machine system (in this case Virtual Box was choosen). 
To make this simulation as fair as possible, we used the same node (an 
Openstack VM vith 32GB of RAM, 8 vCPU and solid state storage) and used the same 
``boot sequence'' for both the VNFs: first we launched the Astaire framework, 
ensuring its availability to process data and then we notified the test 
machine of the successful boot. The startup time was measured from the 
beginning of the startup command (\verb!docker run! for docker and 
\verb!VBoxManage -s! for Virtual Box) till the first TCP hit received by the 
test backend (to make things as smooth as possible, \verb!netcat! was used 
to listen to incoming TCP data).

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[scale=0.4]{docker_vs_vmBarplotGraph}
        \caption{Barplot between Virtual Box and Docker startup times in seconds
          (y-axis).}
        \label{chap:tests:sec:dockervsvb:img:barplot}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[scale=0.35]{docker_vs_vmBoxplotGraph}
        \caption{Boxplot between Virtual Box and Docker with values normalized 
in range $0-1$.}
        \label{chap:tests:sec:dockervsvb:img:boxplot}
    \end{subfigure}
    \caption[Virtual Box vs Docker start up comparison]{In these graphs it is
      possible to see how the total time to start up a virtual machine through
      Virtual Box is very high compared to the time required to the overall
      Docker containers to boot. A single VirtualBox instance requires on
      average 20,211 seconds to boot up, while a container requires, on average,
      only 0.016 seconds. The main reason behind this difference, as already
      explained in other parts of this thesis, it is caused by the guest's
      kernel that has to initialized itself, before starting any program. On
      Docker, instead, the kernel is the same of the host, so the only
      operations needed are to isolate the program from the rest of the OS and
      add it to the process list.}
    \label{chap:tests:sec:dockervsvb:subimg:plots}
\end{figure}

@@

\noindent As is possible to see from the YAML definition, the test involved, for
every launch (that included and $N = 100$, for a total for 1000 tests), the VNF
download from the Docker hub repositories. This, while it forced every node to
delete and download the image for each test, it ensured consistent measurements
in cases where the selected node for the deployment did not have the image
already pulled. In addition to that, another consideration needs to be taken
into account: when the chain consists of two or more elements, the container
image which is used for the container deployment is the same for every VNF
involved, thus reducing the start up time for the subsequent pods that reside in
nodes that have already deployed one.

@@

\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Stamdard deviation (seconds)} & \textbf{Average deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13,291                       \\
\textbf{2}          & 0.6301444                  & 14,207                       \\
\textbf{3}          & 1.14903                    & 15,345                       \\
\textbf{4}          & 3.592179                   & 16,453                       \\
\textbf{5}          & 0.9728132                  & 16,634                       \\
\textbf{6}          & 1.103802                   & 17,418                       \\
\textbf{7}          & 1.561451                   & 18,815                       \\
\textbf{8}          & 0.7698537                  & 20,856                       \\
\textbf{9}          & 1.889197                   & 20,187                       \\
\textbf{10}         & 1.709227                   & 20,476                       \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}

\newpage

\paragraph*{Kubernetes specifications}
A Kubernetes installation was performed in order to carry out the test
descripted above. All the machines (master node and minions) involved had the
same specifications i.e., 4GB of RAM, 2 vCPU and 10GB of SSD storage.
Nonetheless the constrained resources, absolutely far from a real Kubernetes
production environment, is possible to notice how, even with a chain of ten
elements, the average time required to deploy an SFC is equal, if not smaller,
of the time required to deploy a Virtual Box machine on an instance with 32GB of
RAM, 8 vCPU and 50GB of SSD storage.
% graphs, talk about them

@@

In these tests is possible to see one critical aspect concerning an architecture
that follows the containerization approach: great flexibility in terms of
deployments. This possibility to deploy services in the form of SFCs and VNFs in
a very small amount of time is one of the key point required in the new 5G
architecture, that the tests above demonstrated this project is able to adhere.
Finally, the ability to rapidly redeploy software means smooth and easier
software development lifecycle, where developers have the possibility to
automatically push ``fresh'' software in production, letting the MANO and thus
the container orchestrator handling all the difficult and delicate tasks to put
software in a production environment, eliminating the possibility of human
errors and assuring longer uptimes.

>>>>

Regarding the overall system responsivness, a metric we considered worth to 
test was the VNF start up time in a docker environment versus one virtualized 
through a common virtual machine system (in this case Virtual Box was choosen). 
To make this simulation as fair as possible, we used the same node (an 
Openstack VM vith 32GB of RAM, 8 vCPU and solid state storage) and used the same 
``boot sequence'' for both the VNFs: first we launched the Astaire framework, 
ensuring its availability to process data and then we notified the test 
machine of the successful boot. The startup time was measured from the 
beginning of the startup command (\verb!docker run! for Docker and 
\verb!VBoxManage -s! for Virtual Box) till the first TCP hit received by the 
test backend (to make things as smooth as possible, \verb!netcat! was used 
to listen to incoming TCP data).

@@

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[scale=0.4]{docker_vs_vmBarplotGraph}
        \caption{Barplot between Virtual Box and Docker startup times.}
        \label{chap:tests:sec:dockervsvb:img:barplot}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[scale=0.35]{docker_vs_vmBoxplotGraph}
        \caption{Boxplot between Virtual Box and Docker with values normalized 
in range $0-1$.}
        \label{chap:tests:sec:dockervsvb:img:boxplot}
    \end{subfigure}
    \caption[Virtual Box vs Docker start up comparison]{In these graphs it is
      possible to see how the total time to start up a virtual machine through
      Virtual Box is very high compared to the time required to the overall
      Docker containers to boot. A single VirtualBox instance requires on
      average 20,211 seconds to boot up, while a container requires, on average,
      only 0.016 seconds. The main reason behind this difference, as already
      explained in other parts of this thesis, it is caused by the guest's
      kernel that has to initialized itself, before starting any program. On
      Docker, instead, the kernel is the same of the host, so the only
      operations needed are to isolate the program from the rest of the OS and
      add it to the process list.}
    \label{chap:tests:sec:dockervsvb:subimg:plots}
\end{figure}

@@

\noindent As is possible to see from the YAML definition, the test involved, for
every launch (that included and $N = 100$, for a total for 1000 tests), the 
download of the container image from the Docker hub repositories. This, while 
it forced every node to delete and download the image for each test, it ensured 
consistent measurements in cases where the selected node for the deployment did 
not have the image already pulled. In addition to that, another consideration 
needs to be taken into account: when the chain consists of two or more 
elements, the container image which is used for the container deployment is the 
same for every VNF involved, thus reducing the start up time for the subsequent 
pods that reside in nodes that have already deployed one.

@@

\paragraph*{Kubernetes specifications}
A Kubernetes installation was performed in order to carry out the test
descripted above. All the machines involved (master node and minions) had the
same specifications i.e., 4GB of RAM, 2 vCPU and 10GB of SSD storage.
Nonetheless the constrained resources, absolutely far from a real Kubernetes
production environment, it is possible to notice how, even with a chain of ten
elements, the average time required to deploy an SFC is equal, if not smaller,
of the average time required to deploy a Virtual Box machine on an instance 
with 32GB of RAM, 8 vCPU and 50GB of SSD storage.

% TODO is it worth to keep it as a long table?
\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Stamdard deviation (seconds)} & \textbf{Average 
deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13,291                     \\
\textbf{2}          & 0.6301444                  & 14,207                     \\
\textbf{3}          & 1.14903                    & 15,345                     \\
\textbf{4}          & 3.592179                   & 16,453                     \\
\textbf{5}          & 0.9728132                  & 16,634                     \\
\textbf{6}          & 1.103802                   & 17,418                     \\
\textbf{7}          & 1.561451                   & 18,815                     \\
\textbf{8}          & 0.7698537                  & 20,856                     \\
\textbf{9}          & 1.889197                   & 20,187                     \\
\textbf{10}         & 1.709227                   & 20,476                     \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}

@@

In these tests is possible to see one critical aspect concerning an architecture
that follows the containerization approach: great flexibility in terms of
deployments. This possibility to deploy services in the form of SFCs and VNFs in
a very small amount of time is one of the key points required in the new 5G
architecture, that the tests above demonstrated this project is able to adhere.
Finally, the ability to rapidly redeploy software means smooth and easier
software development lifecycle, where developers have the possibility to
automatically push ``fresh'' software to production, letting the MANO and thus
the container orchestrator handling all the difficult and delicate tasks to put
software in a production environment, eliminating the possibility of human
errors and assuring longer uptimes.
